Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-02-14 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
small changes
yny

\section{Discussion}
In this work we investigate the effects of membrane permeability to
water on vesicle hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable vesicle always
inflates to maximize the water content inside the vesicle of a fixed
length (area) in two (three) dimensions. Results from analysis and
numerical simulations show that such relaxation of a semipermeable
vesicle is characterized by a rescaled time $\beta t$. We further
illustrate that the relaxation process consists of at least two phases:
The first phase is dominated by the balance between membrane traction
and viscous stress at early times (up to five minutes), when the vesicle
behaves like an impermeable membrane. The second phase sets in after a
few hours, when water influx begins to dominate and inflate the vesicle.
Over a time scale of more than four weeks, a semipermeable vesicle is
fully inflated, independent of its initial surface-to-volume ratio.

Under strong confinement we show that water permeation can be amplified
on a time scale of a few seconds as a vesicle is squeezed through a
closely-fit channel and a contracting channel. As a semipermeable
vesicle goes through a long closely-fit channel, we observe that the
vesicle loses water at a constant rate, and the longer the channel the
more the loss of water. In the case of a contracting channel, we find
that both permeability and the pressure gradient across the slit must be
sufficiently large for a successful passage. Throughout these
simulations the membrane tension is below the threshold for membrane
poration. Thus we expect the continuum membrane theory to well-capture
the vesicle hydrodynamics, and our simulation results shed light on the
configuration and time scales needed to observe the effects of
permeability on vesicle hydrodynamics under confinement.

>>>>

\section{Discussion}
In this work we investigate the effects of membrane permeability to
water on the membrane hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable inextensible membrane always
inflates to maximize the water content inside the inextensible membrane (a fixed
length (area) in two (three) dimensions.) Results from analysis and
numerical simulations show that such relaxation of a semipermeable
inextensible membrane  is characterized by a rescaled time $\beta t$. We further
illustrate that the relaxation process consists of at least two phases:
The first phase is dominated by the balance between membrane traction
and viscous stress at early times (up to five minutes), when the inextensible membrane
behaves like an impermeable membrane. The second phase sets in after a
few hours, when water influx begins to dominate and inflate the semipermeable membrane.
Over a time scale of more than four weeks, a semipermeable membrane is
fully inflated, independent of its initial surface-to-volume ratio.

Under strong confinement we show that water permeation can be amplified
on a time scale of a few seconds as a semipermeable inextensible membrane is squeezed through a
closely-fit channel and a contracting channel. As a semipermeable
inextensible membrane goes through a long closely-fit channel, we observe lose of water at a constant rate, and the longer the channel the
more the loss of water. In the case of a contracting channel, we find
that both permeability and the pressure gradient across the slit must be
sufficiently large for a successful passage. Throughout these
simulations the membrane tension is below the threshold for membrane
poration. Thus we expect the continuum membrane theory to well-capture
the vesicle hydrodynamics, and our simulation results shed light on the
configuration and time scales needed to observe the effects of
permeability on vesicle hydrodynamics under confinement.
